---
title: "OSC Simulation Study - 1 indicator"
author: "Cho, Young Won"
date: "9/22/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
Create data matrix and loading matrix for fitting fourth-order LDE model  
+ Time Delay Embedding matrix  

Young Won Cho, Sy-Miin Chow   
12/10/2021  

_________________________________________________________________  

## Scenario
Let there be an intensive longitudinal study examining the fluctuation of daily Positive Affect (PA).  
Researchers expect that participant's Gender and Global Marital Satisfaction(MarSat) may influence the dynamics of PA.
* Participants = 100 people
* PA are measured with 5 items but the average score will be used in the analysis;
* Daily items are measured once a day for 100 days (T = 100).
* Thus, data we should have: Person-specific MarSat & Gender(0,1), Within-person 3 items for PA X 100 days  

## measurement model (for person i)
  y_it = tau + lambda*F_it + e_it

[PA1    [t1  [l1         [e1
 PA2  =  t2 + l2 x[*F*] + e2 
 PA3]    t3]  l3]         e3]

[PA1    [t1  [l1          [e1
 PA2  =  t2 + l2 x[*DF*] + e2 
 PA3]    t3]  l3]          e3]
 
[PA1    [t1  [l1           [e1
 PA2  =  t2 + l2 x[*D2F*] + e2 
 PA3]    t3]  l3]           e3]

## structural model
   F2 = int + beta*F1 + resid
-> *D2F* = int + b1*F* + b2*DF* + resid
                             
### OSC Equation
#### Level-1 (time; Within-person)
$d2_PA = int + eta*PA + zeta*d_PA + L1.residuals$  
  + int: baseline (intercept)  
  + eta: frequency parameter  
  + zeta: dampening parameter  

In this simulation, I assume that  
- *baseline* would differ across people depending on MarSat.  
- *eta* would differ depending on Gender (but no random variance).  
- *zeta* would **not** differ across people.  

#### Level-2 (Between-person)  
$int = int0 + 0.3*MarSat + L2.residuals$ (*random variance for intercept; int0 = nu = c(3,4,4))
$eta = -0.5 + .1*Gender + L2residual$ (*no residual variance for eta; the residual variance of eta should be fixed at 0 in mplus)  
$zeta= -0.04$


```{r}
library(deSolve)
library('Matrix') #Containing data generating function for a state-space model
library(truncnorm)
source("C:/Users/yw110/OneDrive/PennState/LDE/LDE_Rscript/1indicator/StateSpaceFunctions.R")
library(ggplot2)
```

### Generating data for the simulation study
```{r}
ny = 1        #Number of manifest indicators
neWithin = 1  #Number of within-person factors
neBetween = 1 #Number of between-person factors

totalPersons <- 150
maxT <- 99	
TimeSeq <- seq(0, maxT, by=1)  # the measurement occasions
# Note: because the time starts from 0, the # of time points we have is '1+maxT' (not maxT)
deltaT <- unique(diff(TimeSeq))
Model <- "Osc" #Multilevel damped oscillator model
```

From now on, we will generate the data of variables.
It's relatively simple to generate covariate1(MarSat) & covariate2(Gennder).
But, it's a bit tricky to make three manifest variables for PA.
Thus, the way we use is: Generate one manifest variable first, then generate the other two, using their relationships.

```{r Step Function}
TVcovType='Step'
#K <- 19        # nr. breakpoints
K=1
N <- 1+maxT   # nr. observations
cov3=c()
for(i in 1:totalPersons){
mu <- c(0,1)#rbinom(2,1,0.5)#rbinom(20,1,0.5) #c(0,1,0,1,0,1,0,1,0,1) # local means
f <- data.frame(cov3=rep(mu, each = N / (K + 1)))
cov3=rbind(cov3,f)
}
cov3<-cov3$cov3
dim(cov3)

DLOmodel <- function(t, prevState, parms) {
     x   <- prevState[1] # x[t]
    dx   <- prevState[2]
    cov3 <- cov3[1+t+(id-1)*(maxT+1)] #cov3[1+t,id]

    with(as.list(parms), {
            dx  <- dx
            d2x <- parms[1]*x + parms[2]*dx + parms[3]*cov3
            res <-c(dx,d2x)
            list(res)
    })
}
#plot(cov3, type='b')
```

### Function for Damped Oscillator model
```{r OU SDE}
#---- Simulate data using damped oscillator model -------
#     with individual differences

#---- TVCOV: OU SDE
TVcovType='OU'
# d(eta) = a*(mu-eta)dt + sigma*dW = (a*mu - a*eta)*dt + sigma*dW
# Thus: A = -a, b = a*mu


# a= 0.03; A = -1*a; mu = 0; b = a*mu
# sigma11 = sqrt(0.05); Q = sigma11^2

# a= 0.03; A = -1*a; mu = 0; b = a*mu
# sigma11 = sqrt(0.1); Q = sigma11^2

# a= 0.1; A = -1*a; mu = 0; b = a*mu  # complex Good
# sigma11 = sqrt(0.18); Q = sigma11^2

a= 0.03; A = -1*a; mu = 0; b = a*mu
sigma11 = sqrt(0.1); Q = sigma11^2 # 0.18

# a= 0.1; A = -1*a; mu = 0; b = a*mu    # complex Good
# sigma11 = sqrt(0.05); Q = sigma11^2

A_del = exp(A*deltaT)
b_del= 1/A*(exp(A*deltaT)-1)*b
#Process noise covariance matrix, 
# Psi = Cov(zeta) = irow{A_hashtag^{-1}[e^A_hashtag*deltaT - I]%*%row(Q)}
A_hashtag = kronecker(A,1) + kronecker(1,A)
Psi = matrix(1/A_hashtag*(exp(A_hashtag*deltaT)-1)*Q)

# #Generate TVcov using the univariate OU model
a0 = runif(totalPersons,-2,2) #Initial condition means
P0 = 0.1  #Initial condition covariance matrix #0.43
R = 0.1 #Measurement error variance
cov3=c()
for(a in a0){
cov3_OU1 = simStateSpaceData(a0=a, P0=matrix(P0), Q=Psi,R=matrix(R),Phi=A_del,Lambda = 1,
                  alpha=b_del,tau = rep(0,1), nt=maxT+1, np=1, ne=1, ny=1, nx=0, npad=0)
cov3<-rbind(cov3,cov3_OU1$stateData)}
dim(cov3)

par(mfrow=c(3,1))
# plot(cov3[1:100], type='b', ylim=c(-3,3)); abline(h=0)
# plot(cov3[101:200], type='b', ylim=c(-3,3)); abline(h=0)
# plot(cov3[201:300], type='b', ylim=c(-3,3)); abline(h=0)

plot(cov3[1:200], type='b', ylim=c(-3,3)); abline(h=0)
plot(cov3[201:400], type='b', ylim=c(-3,3)); abline(h=0)
hist(cov3)
#plot(cov3[401:600], type='b', ylim=c(-3,3)); abline(h=0)

summary(cov3)


# #222
# #Generate TVcov using the univariate OU model
# a0 = 1.5 #Initial condition means
# P0 = 1 #Initial condition covariance matrix #0.43
# R = 0.1 #Measurement error variance
# cov3_OU1 = simStateSpaceData(a0=a0, P0=matrix(P0), Q=Psi,R=matrix(R),Phi=A_del,Lambda = 1,
#                                 alpha=b_del,tau = rep(0,1),#rep(0,ny)
#                                 nt=maxT+1, np=totalPersons/2, ne=1, ny=1, nx=0, npad=0)
# #ne=1 #Number of latent variables;#ny=1 #Number of observed variables
# cov3<-cov3_OU1$stateData
# 
# a0 = -1.5 #Initial condition means
# cov3_OU2 = simStateSpaceData(a0=a0, P0=matrix(P0), Q=Psi,R=matrix(R),Phi=A_del,Lambda = 1,
#                                 alpha=b_del,tau = rep(0,1),#rep(0,ny)
#                                 nt=maxT+1, np=totalPersons/2, ne=1, ny=1, nx=0, npad=0)
# cov3<-rbind(cov3,cov3_OU2$stateData)
# dim(cov3)


# #---- TVCOV: AR(1) model
# TVcovType='AR'
# cov3=c()
# for(i in 1:totalPersons){
#   d<-arima.sim(model=list(ar=0.8), n=(1+maxT),  sd=sqrt(0.1796))
#   cov3<-cbind(cov3, d)
# }
# dim(cov3);cov3=matrix(cov3,ncol=1);dim(cov3)


# Common Model
DLOmodel <- function(t, prevState, parms) {
     x   <- prevState[1] # x[t]
    dx   <- prevState[2]
    cov3 <- cov3[1+t+(id-1)*(maxT+1)] #cov3[1+t,id]

    with(as.list(parms), {
            dx  <- dx
            d2x <- parms[1]*x + parms[2]*dx + parms[3]*cov3
            res <-c(dx,d2x)
            list(res)
    })
}
# To be used in lsoda(), the R-function must be defined as:
# func <- function(t, y, parms,...).
# t is the current time point in the integration,
# y is the current estimate of the variables in the ODE system. 
# parms is a vector or list of parameters
# The return value of func should be a list
```

### Generating one manifest variable of PA for 100 days.
```{r}
#Generate the within-person dynamic part of the data

# time-invariant covariate (e.g., MarSat, gender)
cov1 <- runif(totalPersons,-3,3) #continuous variable.#cov1 <- c(c(-3,-2,-1,1,2,3),runif(totalPersons-6,-2,2))
cov2 <- rbinom(totalPersons,1,.5)-0.5  #Binary variable from a binomial dist (e.g., Gender): 0.5,-0.5
#cov2 <- runif(totalPersons,-2,2)
intcov<-runif(totalPersons,-2,2)


# Empty Matrix
withinFactor <- matrix(NA, nrow=totalPersons, ncol=4+2*(maxT+1)) 
# Because I'll assign [ID, Cov1, Cov2, intCov] into the first 4 columns, the # of columns is "4+2*(maxT+1)"
# one (maxT+1) for cov3, one (maxT+1) for y1
for (id in 1:totalPersons) {
  # Assigning ID, Cov1, Cov2 into the first three columns
  withinFactor[id,1] <- id
  withinFactor[id,2] <- cov1[id]
  withinFactor[id,3] <- cov2[id]
  withinFactor[id,4] <- intcov[id]
  
  # Generating one PA items and assigning them into the 'withinFactor' matrix
  # using lsoda(initial, times, function, parms) # parms: list of parameters used in function
  if (Model=="Osc"){  
      #etaresid<-rnorm(1,0,sqrt(0.02))
      eta = -0.5 #+ ifelse(etaresid>0.4,0.4,etaresid) #+.1*cov2[id]
      zeta= -0.04
      b3  =  0.3 + 0.1*cov1[id] + rnorm(1,0,sqrt(.04)) #+.2*cov1[id]
    parms <- c(eta, zeta, b3)
    
    # xstart<-c(x=rnorm(1,mean=0,sd=1), dx=rnorm(1,mean=0,sd=1), cov3 = runif(1,-4,4)) # OU COV: initial value for x and dx
    # out1 <- as.data.frame(lsoda(xstart, TimeSeq, DLOmodel, parms)) # Solving->getting the simulated data 
    # withinFactor[id,4:(3+(maxT+1))] <- out1$cov3
    
    xstart <- c(x=rnorm(1,mean=0,sd=1), dx=rnorm(1,mean=0,sd=1)) # RandomCov3: initial value for x and dx
    out1 <- as.data.frame(lsoda(xstart, TimeSeq, DLOmodel, parms))
    withinFactor[id,(1+4):(4+(maxT+1))] <- cov3[1:(maxT+1)+(id-1)*(maxT+1)]
    
    # par(mfrow=c(2,1))
    # plot(out1$cov3, type='b')
    #plot(cov3[1:(maxT+1)+(id-1)*(maxT+1)], type='b')
    #plot(out1$x, type='b')
    
    withinFactor[id,(1+4):(4+(maxT+1))+(maxT+1)] <- out1$x #x: repeated measure/ID (wide)
  }}#End of loop through id
colnames(withinFactor) = c("ID","cov1","cov2",'intcov', paste0("cov3",0:maxT), paste0("y",0:maxT))

# Plot the sample of oscillators.
#x11()
par(mfrow=c(3,2))
for (id in sample(1:totalPersons,6)) {
#for (id in 1:6) {
plot(c(min(TimeSeq), max(TimeSeq)), c(-5,5),
     xlab="Time", ylab="Score", main = paste('ID =',id,' cov1=',round(withinFactor[id,'cov1'],2)), type='n')
  lines(c(min(TimeSeq), max(TimeSeq)), c(-0, 0), type='l', lty=2, col=1) # setpoint
  lines(TimeSeq, withinFactor[id,(1+4):(4+(maxT+1))+(maxT+1)], type='b', lwd=2, col=id) # y
  lines(TimeSeq, withinFactor[id,(1+4):(4+(maxT+1))], type='b', lwd=1, col=1) # TV
}
#hist(withinFactor[,"cov30"], breaks = 10)
#hist(withinFactor[,"cov1"], breaks = 10)
```
[Review]  
So far, we have  
- Person-specific Marital Satisfaction  
- Person-specific Gender(0,1)  
- **One** items' values of PA (PA1); measured for 100 days.  

  Within Factor Loadings:  c(1)  
  Between Factor Loadings: c(1)  
  
  Note: I assume Intercept is person-specific. (Thus, 'BF' in mplus is for modeling Intercept)  
  [Intercept]  
  Recall: $int = nu + .5*MarSat + L2.residuals$  
  Thus,  
  $PA1 = nu+ BF                   + F$
  $PA1 = 3 + 1*(.5*Marset + resid)+ F$   
```{r echo=TRUE, eval=FALSE}
# Simulate manifest indicators
y2i = matrix(NA,totalPersons,ny)  #Empty cell for 3-Intercept(Between-person)
y1it = matrix(NA,totalPersons,ny) #Empty cell for 3-WithinFactors
dataMatrix = matrix(NA,totalPersons*(maxT+1),ny) #Empty Matrix for the final result: y2i+y1it
dataMatrix2 = matrix(NA,totalPersons*(maxT+1),ny)

nu = matrix(c(0),ncol=1) # item-specific averages: arbitrary values.
betweenFactorLoadings = matrix(c(1),ncol=neBetween)

withinFactorLoadings = matrix(c(1),ncol=neWithin)
R = diag(c(1))

# element for PA1
InterceptFactors = rep(0,totalPersons)    #no variance at all
#InterceptFactors = rnorm(totalPersons,0,1) #Random variance

#InterceptFactors = 0.3*matrix(intcov, ncol=1) #no random variance
#InterceptFactors = 0.3*matrix(intcov, ncol=1) + rnorm(totalPersons,0,1) # fixed effect + random effect

for (id in 1:totalPersons){
#Between-person effects  #there can be a between person factor, summarizing systematic covariations across PA1, PA2, & PA3 across individuals
y2i[id,] = nu + betweenFactorLoadings %*% InterceptFactors[id]
# by multiplying by between_Factor_Loadings, we're creating the other two values(PA2, PA3).
  # intercept_i = nu0 + nu1(=0.3)*covariate2[ID] + random_i(=rnorm(totalPersons,0,1))
  #               nu0 = nu = c(2,3,4) 따로 나와있으니까 따로 더해주는 것
for (t in 1:(maxT+1)){
y1it[id,] = withinFactorLoadings %*% withinFactor[id,4+(maxT+1)+t] + chol(R)%*%rnorm(ny,0,1)
# by multiplying by within_Factor_Loadings, we're creating the other two values...
  #chol(R)%*%rnorm(ny,0,1) 이거 근데 왜 더해주는 거? 측정 에러...?
dataMatrix[t+(id-1)*(maxT+1),] = y2i[id,] + y1it[id,]
dataMatrix2[t+(id-1)*(maxT+1),] = y1it[id,]
}}
```


```{r PLOTTING, echo=TRUE, eval=FALSE}
par(mfrow=c(2,2))
list<-sample(1:totalPersons,2)
#list=c(45,120)

# for (id in list) {
# plot(c(min(TimeSeq), max(TimeSeq)), c(-3,3),
#      xlab="Time", ylab="Score", main = paste('ID =',id,'\n Simulated data with time-varying covariate'), type='n')
#   lines(c(min(TimeSeq), max(TimeSeq)), c(-0, 0), type='l', lty=2, col=1) # setpoint
#   lines(TimeSeq, withinFactor[id,(1+4):(4+(maxT+1))+(maxT+1)], type='b', lwd=1, col=1) # y
#   lines(TimeSeq, withinFactor[id,(1+4):(4+(maxT+1))], type='b',lwd=0.1, col='blue') # TV
# }


for (id in list) {
plot(c(min(TimeSeq), max(TimeSeq)), c(-5,5),
     xlab="Time", ylab="Score", main = paste('ID =',id,'\n Simulated data'), type='n')
  lines(c(min(TimeSeq), max(TimeSeq)), c(-0, 0), type='l', lty=2, col=1) # setpoint
  lines(TimeSeq, withinFactor[id,(1+4):(4+(maxT+1))+(maxT+1)], type='b', lwd=1, col=id) # y
  #lines(TimeSeq, withinFactor[id,(1+4):(4+(maxT+1))], type='b',lwd=0.01, col='blue') # TV
}

for (id in list) {
plot(c(min(TimeSeq), max(TimeSeq)), c(-5,5),
     xlab="Time", ylab="Score", type='n',main='Data with Fixed Intercept\n (No Between Variance)')
  lines(c(min(TimeSeq), max(TimeSeq)), c(-0, 0), type='l', lty=2, col=1) # setpoint
  #abline(h=y2i[id,],lty=2, col='blue') # setpoint
  lines(TimeSeq, dataMatrix2[(1:100)+(id-1)*(maxT+1),], type='b', lwd=1, col=id) # y
  #lines(TimeSeq, withinFactor[id,(1+4):(4+(maxT+1))], type='b', lwd=1, col='grey') # TV
}

# for (id in list) {
# plot(c(min(TimeSeq), max(TimeSeq)), c(-5,5),
#      xlab="Time", ylab="Score", type='n', main='Data with Random Intercept')
#   lines(c(min(TimeSeq), max(TimeSeq)), c(-0, 0), type='l', lty=2, col=1) # setpoint
#   lines(TimeSeq, dataMatrix[(1:100)+(id-1)*(maxT+1),], type='b', lwd=1, col=id) # y
#   abline(h=y2i[id,],lty=2, col='red') # setpoint
#   #lines(TimeSeq, withinFactor[id,(1+4):(4+(maxT+1))], type='b', lwd=1, col='grey') # TV
# }
```


Now we have RAW data in LONG format.
Thus, with the raw data, we're going to create the data set that will be used in actual analyses.  
  
(0) Raw long format data
(1) Lineally Detrended Data (=linear model's Residuals)  
(2) Raw data in WIDE format  
(3) Time delay embedded Data <- with the RAW data  

```{r}
getwd()
setwd("C:/Users/yw110/OneDrive/PennState/LDE/1209test")
```

```{r}
long = matrix(NA,totalPersons*(maxT+1),2+ny+1)
for (id in 1:totalPersons){ 
  long[(1:(maxT+1))+(id-1)*(maxT+1),1] = id
  long[(1:(maxT+1))+(id-1)*(maxT+1),2] = TimeSeq
  long[(1:(maxT+1))+(id-1)*(maxT+1),2+(1:ny)] = dataMatrix[(1:(maxT+1))+(id-1)*(maxT+1),]  # y1
  long[(1:(maxT+1))+(id-1)*(maxT+1),2+ny+1]   = withinFactor[id, (1+4):(4+maxT+1)] # cov3
  #s<-summary(long[(1:(maxT+1))+(id-1)*(maxT+1),3:6])
  #print(s[4,])
}
s<-summary(long[,3:(2+ny+1)]); s

# For the simulation, we are going to use the raw data before detrending, so we can model individual differences in intercepts.
colnames(long) = c("ID","Time", paste0("y",1:ny),'TVcov')
long = data.frame(long, cov1=rep(withinFactor[,"cov1"],each=(maxT+1)),
                        cov2=rep(withinFactor[,"cov2"],each=(maxT+1)),
                      intcov=rep(withinFactor[,"intcov"],each=(maxT+1)))
head(long)
write.table(round(long,5), file=paste0(Model,"Raw_long.txt"), append=F,
            row.names=FALSE,col.names=TRUE,sep=",")
```

####-- (1) Lineally Detrended Data --####
```{r eval=FALSE}
# Detrended y, not TVcov
theResiduals = matrix(NA,totalPersons*(maxT+1),2+ny+1)
for (id in 1:totalPersons){ 
  theResiduals[(1:(maxT+1))+(id-1)*(maxT+1),1] = id
  theResiduals[(1:(maxT+1))+(id-1)*(maxT+1),2] = TimeSeq
  theResiduals[(1:(maxT+1))+(id-1)*(maxT+1),2+(1:ny)] = lm(dataMatrix[(1:(maxT+1))+(id-1)*(maxT+1),] ~ TimeSeq)$residuals
  theResiduals[(1:(maxT+1))+(id-1)*(maxT+1),2+ny+1]   = withinFactor[id, 4:(3+maxT+1)] # cov3
}
summary(theResiduals[,3:(2+ny+1)])
summary(theResiduals[(1:(maxT+1))+(id-1)*(maxT+1),3:(2+ny+1)]) #Check: the means of "individual (last id)" = 0

colnames(theResiduals) = c("ID","Time",paste0("y",1:ny),'TVcov')
theResiduals = data.frame(theResiduals,
                          cov1=rep(withinFactor[,"cov1"],each=(maxT+1)),
                          cov2=rep(withinFactor[,"cov2"],each=(maxT+1)),
                        intcov=rep(withinFactor[,"intcov"],each=(maxT+1)))
head(theResiduals)
write.table(round(theResiduals,5), file=paste0(Model,"Residuals.txt"), append=F,
            row.names=FALSE,col.names=TRUE,sep=",")
```

####-- (2) Wide format - RAW DATA (no detrending) --####
```{r eval=FALSE}
# Reshape the long-format to the Wide-format
# This procedure was done for the raw data to be used in Mplus.
library(reshape2)
melted<-melt(long, id.vars=c("ID", "Time",'cov1','cov2','intcov'))
wide<-dcast(melted, ID+cov1+cov2+intcov~variable+Time)
names(wide)

# Save the wide format raw data
write.table(round(wide,5), file=paste0(Model,"Raw_wide.txt"), append=F,
            row.names=FALSE, col.names=FALSE, sep=",")
```

####-- (3) Time delay embedded Data --####
```{r eval=FALSE}
require('plyr') # for 'ddply' function

#Read in data set
#OscData = read.table(file="OscResiduals.txt",sep=",",header=TRUE) ; Type='Resid'
OscData = read.table(file="OscRaw_long.txt",sep=",",header=TRUE); Type='Raw'

colnames(OscData)
head(OscData)
ny = 1 #Number of manifest variables
nPerson = length(unique(OscData$ID)) #Number of participants = 50

tau = 1     # The lag between subsequent columns in the embedded matrix
deltaT = 1  # The amount of time elapsed between subsequent observations
embedD = 6  # The number of columns in the time-delay embedded matrix

#---- Create a time delay embedded data ----
# Time delay embedding function
Embed = function(x, E, tau) {  
  len = length(x)
  out = x[1:(len-(E*tau)+tau)]
  for(i in 2:E) { out = cbind(out,x[(1+((i-1)*tau)):(len-(E*tau)+(i*tau))]) }
  return(as.matrix(out))
}
#Use column bind (cbind) the output of embedding each ID's data in turn
embedMultiPerson = function(x,E,tau,variableNames){
  for (j in 1:length(variableNames)){
    x_temp = x[,c("ID",variableNames[j])]
    colnames(x_temp)[2] = 'y'
    if (j==1){
      out = as.matrix(ddply(x_temp, .(ID), here(summarise),
                            Embed(y,E,tau)))}
    else{
      out = cbind(out,as.matrix(ddply(x_temp, .(ID), here(summarise),
                                      Embed(y,E,tau))[,2]))
    }}
  return(out)
}

#Use do.call to column bind (cbind) the output of embedding
lnames = c("y1","TVcov")
#The embedMultiPerson function will look for a variable called "ID" in doing the embedding action by person.
# So, there should be a variable called 'ID'
embedAll = embedMultiPerson(OscData[,c("ID",lnames)],embedD, tau,lnames)

colnames(embedAll) = c("ID",paste0("y1lag",(embedD-1):0), paste0("TVlag",(embedD-1):0))
colnames(embedAll)
dim(embedAll); dim(OscData)
embedAll = data.frame(embedAll)
embedAll$cov1 = OscData$cov1[OscData$Time >= embedD-1]
embedAll$cov2 = OscData$cov2[OscData$Time >= embedD-1]
embedAll$intcov = OscData$intcov[OscData$Time >= embedD-1]
#How did we get from 5000 to 4750 rows?
#We lost embedD(6) - 1 = 5 rows everytime we do time delay embedding on each person,
#(n = 50). So we still have:
#5000-(nPerson*(embedD-1)) = 4750 rows

head(embedAll)
Model="Osc"
write.table(round(embedAll,5), file=paste0(Model,Type,"_TDelay",embedD,"_",TVcovType,"_n",totalPersons,".txt"), append=F,
            row.names=FALSE, col.names=FALSE, sep=",")
```

# Create the fixed LDE loading matrix ----
```{r}
get_LDE_LoadingMatrix <- function(E, tau, deltaT, order=4) {
  L = rep(1,E)
  for(i in 1:order) {
    L = cbind(L,(((c(1:E)-mean(1:E))*tau*deltaT)^i)/factorial(i)  ) 
  }
  return(L) 
}
Embedding= 8
derivOrder = 1 #Highest derivative order in the LDE model
LDE.Loading = get_LDE_LoadingMatrix(E=Embedding,tau=1,deltaT=1,order=derivOrder)
LDE.Loading

```

g matrix.
get_LDE_LoadingMatrix <- function(E, tau, deltaT, order=4) {
  L = rep(1,E)
  for(i in 1:order) {
    L = cbind(L,(((c(1:E)-mean(1:E))*tau*deltaT)^i)/factorial(i)  ) 
  }
  return(L) 
}
Embedding=6
derivOrder = 4 #Highest derivative order in the LDE model
LDE.Loading = get_LDE_LoadingMatrix(E=Embedding,tau=1,deltaT=1,order=derivOrder)
LDE.Loading

```

